\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{fontawesome5}
\usepackage{multicol}
\input{glyphtounicode}

% Adjust page margins
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\setlength{\footskip}{6pt}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Set page dimensions
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

% URL style
\urlstyle{same}

% Text alignment
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
% Use small caps with medium series to avoid missing bx/sc shape
\newcommand{\scbold}{\scshape\fontseries{m}\selectfont}
\titleformat{\section}
  {\vspace{-4pt}\raggedright\large\bfseries\scbold}
  {}
  {0em}
  {}
  [\color{black}\titlerule \vspace{-5pt}]

% Ensure Unicode compatibility for PDF
\pdfgentounicode=1

% (No bold small caps in Latin Modern; using medium small caps via \scbold)

% Fallback for missing bold small caps in Latin Modern (map bx/b sc -> m sc)
\makeatletter
\DeclareFontShape{T1}{lmr}{bx}{sc}{<->ssub * lmr/m/sc}{}
\DeclareFontShape{T1}{lmr}{b}{sc}{<->ssub * lmr/m/sc}{}
\makeatother

% ----- Custom Commands -----
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Project heading that wraps long titles and moves the button to next line
\newcommand{\resumeProjectHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{1.0\textwidth}[t]{X r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx}\vspace{-7pt}
}

% ----- Document Start -----
\begin{document}

%----------HEADER----------
\begin{center}
    {\Huge \scshape Madhav Gautam} \\ \vspace{1pt}
    \small
    \faPhone\ +91-8309491739 ~
    \href{mailto:mxdhavgautam@gmail.com}{\faEnvelope\ mxdhavgautam@gmail.com} ~
    \href{https://linkedin.com/in/mxdhavgautam}{\faLinkedin\ linkedin.com/in/mxdhavgautam} ~
    \href{https://mxdhavgautam.com}{\faGlobe\ mxdhavgautam.com}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{2021 -- 2025}
      {B.Tech in Computer Science (Specialization: AI and Robotics)}{Chennai, India}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {Society Complaint Management System}
      {}
      {Python, MySQL}
      {\href{https://github.com/mxdhavgautam/SocietyComplaintManagementSystem}{\faGithub~View on GitHub}}
      \resumeItemListStart
        \resumeItem{Built a complaint management system in Python and MySQL for tracking, status updates, and resolution workflow.}
        \resumeItem{Added error handling and file backups to keep records safe and improve the user experience.}
        \resumeItem{Replaced manual registers with a simple digital process to improve accuracy and speed up resolution.}
      \resumeItemListEnd

    % Layout fix: wrap long title and place the GitHub button on the next line
    \resumeProjectHeading
      {A Comparative Study of Deep Learning Models and Training Techniques for Cardiac MRI Classification}
      {}
      {Python, TensorFlow, Keras}
      {\href{https://github.com/mxdhavgautam/A-Comparative-Study-of-Deep-Learning-Models-and-Training-Techniques-for-Cardiac-MRI-Classification}{\faGithub~View on GitHub}}
      \resumeItemListStart
        \resumeItem{Compared CNNs (MobileNetV2, ResNet152V2, DenseNet201, InceptionV3) on \(\sim\)63k CMRI images; internal 80/20 split via \texttt{ImageDataGenerator} with rescaling and augmentation at 128\(\times\)128.}
        \resumeItem{Used transfer learning (frozen base encoders), class weighting for imbalance, a simple spatial attention block, and an attention probability‑averaging ensemble.}
        \resumeItem{Trained with Adam (LR \(1\text{e-}4\)), Binary Crossentropy; callbacks: EarlyStopping, ReduceLROnPlateau, ModelCheckpoint (best \texttt{val\_loss}).}
        \resumeItem{Reported balanced accuracy, per‑class precision/recall/F1, and confusion matrices; best validation from the attention ensemble (acc \(\sim\)0.778, balanced acc \(\sim\)0.772).}
        \resumeItem{Single‑notebook pipeline with saved checkpoints (.keras) and history plots; heavy ResNet checkpoints excluded due to size limits, regenerable from the notebook.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CR3ATE.AI}{Jan 2025 -- Present}
      {Developer Intern (ML, CV, iOS, Backend)}{United States, Remote}
      \resumeItemListStart
        \resumeItem{Built and tuned CoreML models (MobileNetV3, EfficientNet) for real‑time blur detection on iOS; converted TensorFlow/Keras models to CoreML and integrated with Swift/SwiftUI camera flows.}
        \resumeItem{Shipped the production iOS app and the web app/backend for \href{https://cr3ate.ai}{cr3ate.ai}. Implemented secure file upload and results retrieval using Nest.js APIs, AWS Lambda, and Amazon S3 presigned URLs; used Firebase Authentication.}
        \resumeItem{Developed Dockerized backend services (Nest.js, MongoDB) with strict JSON parsing and error handling to improve API reliability.}
        \resumeItem{Connected the Hive API to trigger 3D Gaussian splat reconstructions, enabling ML‑driven AR/VR workflows.}
        \resumeItem{Worked with ML engineers to align training/evaluation with app needs, including model export and on‑device checks.}
      \resumeItemListEnd

    \resumeSubheading
      {HCLTech}{Oct 2023 -- Dec 2023}
      {Software Development Intern (Flutter)}{Lucknow, India}
      \resumeItemListStart
        \resumeItem{Shipped an accessibility‑first Flutter app that guides seniors through common smartphone tasks with clear steps, large text, and high‑contrast themes.}
        \resumeItem{Simplified navigation and increased touch targets; incorporated user feedback in short Agile cycles to reduce confusion and improve usability.}
        \resumeItem{Handled end‑to‑end work: basic UI/UX design, implementation, testing, and delivery for pilot use; focused on clarity and ease of use.}
      \resumeItemListEnd

    \resumeSubheading
      {WESEE - Weapons \& Electronics Systems Engineering Establishment}{Aug 2023 -- Sep 2023}
      {Software Development Life Cycle (SDLC) Intern}{Ministry of Defence, New Delhi}
      \resumeItemListStart
        \resumeItem{Built communication apps in Qt/Qt Creator that send and receive data over UDP/TCP/IP, with offline storage using SQLite.}
        \resumeItem{Added receiver‑side validation and control logic to run only approved commands; aimed for predictable and stable behavior.}
        \resumeItem{Integrated new modules into existing systems without breaking current workflows, operating in a secure, resource‑limited setup.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:} Python, Java, C, C++, HTML, Dart, SQL (MySQL, SQLite), Bash/Zsh \\
     \textbf{Machine Learning \& Data Science:} TensorFlow, Keras, CoreML, Scikit-learn, Pandas, NumPy, Matplotlib, Google Colab \\
     \textbf{Frameworks \& Technologies:} Nest.js, Flutter, UIKit, SwiftUI, Qt, Robot Operating System (ROS) \\
     \textbf{Cloud \& Infrastructure:} AWS Lambda, Amazon S3, Docker, Firebase Authentication, MongoDB \\
     \textbf{Developer Tools \& Others:} VS Code, Git, GitHub, QtCreator, Postman, Microsoft Excel
    }}
\end{itemize}

%-----------LEADERSHIP / EXTRACURRICULAR-----------
\section{Leadership / Extracurricular}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Voyage E‑Summit 2024}{Jan 2024 -- Aug 2024}
      {Admin — Social Media and Content Head}{VIT Chennai}
      \resumeItemListStart
        \resumeItem{Managed content planning and publishing across channels; coordinated speaker announcements, event updates, and schedules for the hackathon, startup conclave, and mentoring sessions.}
        \resumeItem{Partnered with event and design teams to keep messaging clear and consistent; ensured timely posts before and during the summit.}
      \resumeItemListEnd

    \resumeSubheading
      {IEEE Computer Society, VIT Chennai}{Jan 2024 -- Sep 2024}
      {Advisory Board Member, Design Head}{}
      \resumeItemListStart
        \resumeItem{Led planning and execution for UI/UX, social media, and visual design across chapter initiatives to improve brand consistency and engagement.}
        \resumeItem{Mentored team leads on project coordination, content strategy, and community growth.}
        \resumeItem{Supported outreach events and technical workshops to increase chapter visibility and student participation.}
      \resumeItemListEnd

    \resumeSubheading
      {Enactus (VIT Chennai)}{Mar 2022 -- Jan 2024}
      {Video Editor — Creative Team}{}
      \resumeItemListStart
        \resumeItem{Edited videos for campaigns and events; collaborated with the creative team on concepts, storyboards, and delivery timelines.}
        \resumeItem{Kept visuals clear and on‑brand; prepared final cuts for publishing and event use.}
        \resumeItem{Created and edited the video that propelled the chapter to being the Runner-Ups at Enactus Nationals 2022.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

% ----- Document End -----
\end{document}